Physics of Tidal Dissipation in Early-Type Stars and White Dwarfs: Hydrodynamical Simulations of Internal Gravity Wave Breaking in Stellar Envelopes

### 2020-05-23 writeups/Su_IGW_break.tex
use MNRAS video link

A full video of our simulation with $N_x = 768$, $N_z = 3072$, $\mathrm{Re} =
1024$ is available
online\footnote{\url{http://www.princeton.edu/\~lecoanet/data/breaking\_wave.mov}}. We
take this to be our fiducial simulation for the remainder of this paper, though
other simulations show qualitatively similar behavior.

>>>>

A full video of our simulation with $N_x = 768$, $N_z = 3072$, $\mathrm{Re} =
1024$ is available
online\footnote{\url{https://academic.oup.com/mnras/article-abstract/495/1/1239/5835700#supplementary-data}}.
We take this to be our fiducial simulation for the remainder of this paper,
though other simulations show qualitatively similar behavior.
